---
title: "1_kinnert test 2"
author: "Tal Gavriely"
date: "June 22, 2020"
output: 
   prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

##take the simple model from Kinneret test.Rmd and try to add some conditions


```{r message=FALSE, warning=FALSE}
library(sf)
library(raster)
library(ggplot2)
library(dplyr)
library(tidyr)

#library(rgdal)
#library(rgeos)
#library(remotes)
#install_github("mtennekes/tmaptools")
#install_github("mtennekes/tmap")
#install.packages('rgdal', type="source")
```


#functions:

1. fishing function


```{r}
fishing<-function(fish_data,fishermen_data,fishing_efficiency = 0.7,fishers_max=100){
 
 
fish_data <-fish_data %>%
  mutate("catch"= rbinom(nrow(fish_data),
                         as.integer(fish_data$fish_density_start),
                         fishing_efficiency)) # set the catch acording to the binominal distrabution

fish_data$catch<-ifelse(fish_data$catch>fishers_max,fishers_max,fish_data$catch) # set the maximum capcity
   
fish_data$fish_density_start[fish_data$location %in% fishermen$location]<-fish_data$catch[fish_data$location %in% fishermen$location] #change the fish denstiy (for the next step)

fishermen_data$catch<-fish_data$fish_density_start[fishermen_data$location] #record it in the fishers data

output<-list(fish_data,fishermen_data)
return(output)

}

```

2. fishermen movement


calculate the catch of each fishermen. if the catch is higher then the mean of all fishermen stay at the same place, if it lower choose new random location


```{r}

fisher_move<-function(fish_data,fishermen_data,fishing_efficiency){
  
fishermen_data$catch<-fish_data$fish_density_start[fishermen_data$location]*fishing_efficiency
  
mean_catch<-mean(fishermen_data$catch)

fishermen_data$location<-ifelse(fishermen_data$catch>mean_catch,
       fishermen_data$location,
       sample(1:nrow(fish_data)))

return(fishermen_data)
return(mean_catch)

}


```




3. plot the fish density and the fishermen location and the fish density


```{r}
plot_fisher<-function(fish_data,fishermen_data){
  
 fisher_grid<- left_join(fishermen_data,fish_data,by="location")
 fisher_grid<- st_as_sf(fisher_grid)
 fishermen_map<-ggplot() + geom_sf(data = fish_data,aes(fill=fish_density_start))+
  geom_sf(data = fisher_grid,aes(colour = "red",fill = fish_density_start))+
  geom_sf_label(data= fisher_grid,aes(label = fishermen_id), label.padding = unit(0.1, "mm"))
 
 return(fishermen_map)
  
  
}
```

4. function that determine which map to use (in cases like season ect.)

```{r}


fish_data_list<-list(grid_data,grid_data_2,grid_data_3)

change_map<-fuction(fish_data_list,change_after = 10){
  
  all_change_point<- data.frame("number"=seq(1:length(fish_data_list)))
  all_change_point<- all_change_point %>%  mutate("change_point" = number * change_after)
  
}


```


```{r}

number<-39
change_after<-10

all_change_point<- data.frame("number"=seq(1:length(fish_data_list)))

all_change_point<- all_change_point %>%  mutate("end" = number * change_after)

all_change_point<-all_change_point %>%  mutate("start" = end - change_after)


all_change_point$ok<-ifelse(number > all_change_point$start & number <= all_change_point$end,
                            "Take this",
                            "no")

all_change_point$ok[nrow(all_change_point)] <- if(length(unique(all_change_point$ok))==1,"Take this","no")



#all_change_point<-all_change_point %>%  mutate("ok" = ((number > diff) & (number < change_point))
                                               
                                               

```


upload the kinneret shapefile

```{r}
Kinneret<-st_read("kinneret polygon self based on bing WGS 84.shp")

```

Create a grid (ploygon) in the shape of kinneret lake (for a start ill create 3 grids)

```{r}
grid_1 <- Kinneret %>% 
  st_make_grid(cellsize = 500) %>% # grid of 500m on 500m
  st_intersection(Kinneret) # cut it to the shape of the kinneret poligon

```


add to the polygon grid data of cell Id and fish density

```{r}

data <-data.frame("location" =1:length(grid_1),fish_density_start=seq(1:729))
data_2<-data.frame("location" =1:length(grid_1),fish_density_start=c(seq(1:365),c(364:1)))
data_3<-data.frame("location" =1:length(grid_1),fish_density_start=seq(729:1))

grid_data<- st_sf(data, geometry = grid_1) 
grid_data_2<- st_sf(data_2, geometry = grid_1) 
grid_data_3<- st_sf(data_3, geometry = grid_1)

plot(grid_data["fish_density_start"])
plot(grid_data_2["fish_density_start"])
plot(grid_data_3["fish_density_start"])
```



set the fishermen data

```{r}

fishermen<-data.frame("fishermen_id"=1:50)
fishermen$location<-sample(1:nrow(grid_data),nrow(fishermen),replace = F)
fishermen$catch<-rep(0)

plot_fisher(grid_data,fishermen)

```


```{r}


time_steps <- 30
ts <- 0
number<-1
plot_list<-list()

while(ts < time_steps){
    grid_data <- fishing(fish_data =  grid_data,fishermen_data =  fishermen,fishing_efficiency =  0.3);
    fishermen<-fisher_move(fish_data = grid_data,fishermen_data = fishermen,fishing_efficiency =  0.3);
    plot_list[[number]]<-plot_fisher(grid_data,fishermen);
    ts   <- ts + 1
    number<-number+1
}
 
plot_list[[1]] 
plot_list[[2]]
plot_list[[3]]
plot_list[[4]]
plot_list[[5]] 
plot_list[[6]]
plot_list[[7]]
plot_list[[8]]
plot_list[[9]] 
plot_list[[10]]


```