---
title: "1_kinnert test 1"
author: "Tal Gavriely"
date: "June 22, 2020"
output: 
   prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

##take the simple model from Kinneret test.Rmd and try to add some conditions


```{r message=FALSE, warning=FALSE}
library(sf)
library(rgeos)
library(raster)
#install.packages('rgdal', type="source")
library(rgdal)
library(ggplot2)
library(dplyr)
library(tidyr)
#library(remotes)
#install_github("mtennekes/tmaptools")
#install_github("mtennekes/tmap")

```


functions:

1. fishing function

take the fish density and reduce it by the fishing efficiancey if there is a fishermen on the same spot

*note: if the fishing efficiency is 0.7 from 100 fish, 70 will be the catch and 30 will stay in the water.


```{r}
fishing<-function(fish_data,fishermen_data,fishing_efficiency){
  
fish_data$fish_density_start[fish_data$location %in% fishermen$location]<-fish_data$fish_density[fish_data$location %in% fishermen$location ]*(1-fishing_efficiency) 

return(fish_data)

}

```

2. fishermen movement


calculate the catch of each fishermen. if the catch is higher then the mean of all fishermen stay at the same place, if it lower choose new random location


```{r}

fisher_move<-function(fish_data,fishermen_data,fishing_efficiency){
  
fishermen_data$catch<-fish_data$fish_density_start[fishermen_data$location]*fishing_efficiency
  
mean_catch<-mean(fishermen_data$catch)

fishermen_data$location<-ifelse(fishermen_data$catch>mean_catch,
       fishermen_data$location,
       sample(1:nrow(fish_data)))

return(fishermen_data)
return(mean_catch)

}






```


trail

```{r eval=FALSE, include=FALSE}
sample_adjecent_cells<-function(cell_id,buffer_dist=499,fish_data)  {
  
  cell<-which(fish_data$location == cell_id)
  
  buffer<-st_buffer(fish_data[cell,1],buffer_dist)
  
  buffer$location<-NULL
  
  inside<- st_intersection(buffer, fish_data)
  
  choose_from_here<-which(fish_data$location %in% inside$location)
  
  choose_from_here<-as.numeric(choose_from_here)
  
  new_location<- sample(choose_from_here,1,replace = F)
  
  return(new_location)
  
}

fisher_move<-function(fish_data,fishermen_data,fishing_efficiency){
  
fishermen_data$catch<-fish_data$fish_density_start[fishermen_data$location]*fishing_efficiency
  
mean_catch<-mean(fishermen_data$catch)

fishermen_data$location<-ifelse(fishermen_data$catch>mean_catch,
       sample_adjecent_cells(cell_id = fishermen_data$location,buffer_dist =  499,fish_data= fish_data),
       sample(1:nrow(fish_data)))

return(fishermen_data)


}


sample_adjecent_cells(fishermen$location[1],499,fish_data = grid_data)


adjecent_cells(fishermen_location = fishermen$location)

fishermen$location<-ifelse(fishermen$fishermen_id>3,
                           sample_adjecent_cells(cell_id = fishermen$location,
                                                 buffer_dist = 499,
                                                 fish_data = grid_data),
                           sample(1:100)
                           )


#cell<-which(grid_data$location==fishermen$location[3])

#buff<-st_buffer(grid_data[cell,1], dist = 499)
#buff$location<-NULL

#plot(grid_data["location"],reset = FALSE)
#plot(buff, col = "red",add=TRUE)

#inside<-st_intersection(buff, grid_data)



#plot(grid_data["location"],reset = FALSE)
#plot(inside,col="red",add=TRUE)
```



3. plot the fish density and the fishermen location and the fish density


```{r}
plot_fisher<-function(fish_data,fishermen_data){
  
 fisher_grid<- left_join(fishermen_data,fish_data,by="location")
 fisher_grid<- st_as_sf(fisher_grid)
 fishermen_map<-ggplot() + geom_sf(data = fish_data,aes(fill=fish_density_start))+
  geom_sf(data = fisher_grid,aes(colour = "red",fill = fish_density_start))+
  geom_sf_label(data= fisher_grid,aes(label = fishermen_id), label.padding = unit(0.1, "mm"))
 
 return(fishermen_map)
  
  
}
```

upload the kinneret shapefile

```{r}
Kinneret<-st_read("kinneret polygon self based on bing WGS 84.shp")

```

Create a grid (ploygon) in the shape of kinneret lake 

```{r}
grid_1 <- Kinneret %>% 
  st_make_grid(cellsize = 500) %>% # grid of 500m on 500m
  st_intersection(Kinneret) # cut it to the shape of the kinneret poligon


```


add to the polygon grid data of cell Id and fish density

```{r}

data<-data.frame("location" =1:length(grid_1),fish_density_start=seq(1:729))

grid_data<- st_sf(data, geometry = grid_1) 


```



set the fishermen data

```{r}

fishermen<-data.frame("fishermen_id"=1:50)
fishermen$location<-sample(1:nrow(grid_data),nrow(fishermen),replace = F)
fishermen$catch<-rep(0)

plot_fisher(grid_data,fishermen)

```


```{r}


time_steps <- 30
ts <- 0
number<-1
plot_list<-list()

while(ts < time_steps){
    grid_data <- fishing(fish_data =  grid_data,fishermen_data =  fishermen,fishing_efficiency =  0.3);
    fishermen<-fisher_move(fish_data = grid_data,fishermen_data = fishermen,fishing_efficiency =  0.3);
    plot_list[[number]]<-plot_fisher(grid_data,fishermen);
    ts   <- ts + 1
    number<-number+1
}
 
plot_list[[1]] 
plot_list[[2]]
plot_list[[3]]
plot_list[[4]]
plot_list[[5]] 
plot_list[[6]]
plot_list[[7]]
plot_list[[8]]
plot_list[[9]] 
plot_list[[10]]


```